Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-04-19 docs/00-manuscripts/ieee/ieee-manuscript.tex
wording: rephrase side analysis

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

@@

where \(H\) is the conditional entropy of the response variable (class) or the feature (attribute), respectively.
To be able to use this method with a numeric response (defoliation in our case), the variable is discretized into equal bins and treated as a class variable.
While the number of bins can be treated as a hyperparameter of the filter method, we decided to use \texttt{\(n_{bin}\) = 10} after rank correlations of $> 0.9$ for different bin sizes were observed in a side analysis.

@@

% permutation based var imp for datasets HR and VI
\begin{figure*} [t!]
	\centering
	\begin{center}
		\includegraphics[width=0.98\textwidth] {fi-permut-vi-hr-1.pdf}
		\caption{Variable importance for feature sets HR and VI: Mean decrease in RMSE for one-hundred feature permutations using the SVM learner. The wavelength range on the x-axis matches the range of the hyperspectral sensor (400 nm - 1000 nm). For each dataset, the ten most important features were highlighted as black dots and labeled by name. Grey dots represent features from importance rank 11 to last. The spectral signature (mean) of each plot was added as a reference on a normalized reflectance scale [0, 1] (secondary y-axis). VI features were decomposed into their individual formula parts; all instances being connected via dashed lines. Each VI feature is composed out of at least two instances.}\label{fig:fi-permut-vi-hr}
	\end{center}
\end{figure*}

@@

\begin{figure} [ht]
	\begin{center}
		\includegraphics[width=0.48\textwidth] {fi-vi-ale-1.pdf}
		\caption{ALE plots on dataset VI of SVM learner. Subset showing the ten most important features according to the permutation-based variable importance. The y-axis shows the deviation to the mean prediction for each feature, with the mean prediction being centered at zero.}\label{fig:fi-vi-ale}
	\end{center}
\end{figure}

>>>>

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to Gbe placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

@@

where \(H\) is the conditional entropy of the response variable (class) or the feature (attribute), respectively.
To be able to use this method with a numeric response (defoliation in our case), the variable is discretized into equal bins and treated as a class variable.
While the number of bins can be treated as a hyperparameter of the filter method, we decided to use \texttt{\(n_{bin}\) = 10} after rank correlations of $> 0.9$ for different bin sizes were observed during data exploration.

@@

% permutation based var imp for datasets HR and VI
\begin{figure*} [ht!]
	\centering
	\begin{center}
		\includegraphics[width=0.9\textwidth] {fi-permut-vi-hr-1.pdf}
		\caption{Variable importance for feature sets HR and VI: Mean decrease in RMSE for one-hundred feature permutations using the SVM learner. The wavelength range on the x-axis matches the range of the hyperspectral sensor (400 nm - 1000 nm). For each dataset, the ten most important features were highlighted as black dots and labeled by name. Grey dots represent features from importance rank 11 to last. The spectral signature (mean) of each plot was added as a reference on a normalized reflectance scale [0, 1] (secondary y-axis). VI features were decomposed into their individual formula parts; all instances being connected via dashed lines. Each VI feature is composed out of at least two instances.}\label{fig:fi-permut-vi-hr}
	\end{center}
\end{figure*}

@@

% \begin{figure} [ht]
% 	\begin{center}
% 		\includegraphics[width=0.48\textwidth] {fi-vi-ale-1.pdf}
% 		\caption{ALE plots on dataset VI of SVM learner. Subset showing the ten most important features according to the permutation-based variable importance. The y-axis shows the deviation to the mean prediction for each feature, with the mean prediction being centered at zero.}\label{fig:fi-vi-ale}
% 	\end{center}
% \end{figure}
